Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
change color from yellow to gray in figure 1

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta_p G_s$}};
   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

>>>>

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta_p G_s$}};
   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };
